R Notebook

### 2019-08-30 src/testing_file.Rmd

}
  rd <- rbind(rd1, rd3, rd4, rd5, rd6, rd7, rd8, rd9, rd10, rd11, rd12)
    #rd <- as.data.frame(rd)
    #rd$month <- as.factor(rd$month)
p <- ggplot(rd, aes(x=month, y = prob)) + geom_violin(trim=FALSE)
plot(p)

@@

```{r}
predjan <- read.csv("../output/maxent/all_data/testforslr_jan.csv", header = TRUE)
predjanpr <- subset(predjan, occurrence == 1)
plot(predjanpr$temp_depth, predjanpr$predicted)
predjanbk <- subset(predjan, occurrence == 0)
plot(predjanbk$temp_depth, predjanbk$predicted)
```

@@

mont <- 
data_aeaX <- read.csv("../output/maxent/all_data/testforslr_jan.csv", header = TRUE)
data_aeaX$predicted_mthdata <- NA

xy <- data_aeaX[ ,c(19,20)] # This is to tell R where the coordinates are (in column 18 and 19). Note that the column order needs to be longitude, latitude
data_aea_sp <- SpatialPointsDataFrame(coords = xy, data = data_aeaX, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
avgasc_list <- list.files(paste0("../output/maxent/predictions/jan"), pattern = "^avg_.*.asc", full.names = TRUE) #true means the full path is included
for (j in 1:nrow(data_aea_sp)) { 
for (i in 1:length(avgasc_list)) {  
 de <- data_aea_sp$depthlyr_mod[j]  # a variable for the observation depth layer
  rasdep <- str_sub(avgasc_list[i], 46, -5)
       if (rasdep == de){
          temp_brick <- raster(avgasc_list[i])
        crs(temp_brick) <- aea@crs 
              data_aea_sp$predicted_mthdata[j] <- extract(x=temp_brick, y = data_aea_sp[j, ])

@@

write.csv(data_aea1, "../output/maxent/all_data/predictions_jan.csv", row.names = FALSE)
 #}

@@

```{r}
predjul <- read.csv("../output/maxent/all_data/predictions_jul.csv", header = TRUE)
plot(predjul$occurrence, predjul$predicted_mthdata)
plot(predjul$occurrence, predjul$predicted_alldata)
```

@@

>>>>

}
  #rd <- rbind(rd1, rd3, rd4, rd5, rd6, rd7, rd8, rd9, rd10, rd11, rd12)
  rd <- rbind(rd1, rd3, rd4)

    #rd <- as.data.frame(rd)
    #rd$month <- as.factor(rd$month)
p <- ggplot(rd, aes(x=month, y = prob)) + geom_violin(trim=FALSE)
plot(p)

@@

```{r}
predjan <- read.csv("../output/maxent/all_data/pred_file_jan.csv", header = TRUE)
predjanpr <- subset(predjan, occurrence == 1)
predjanbk <- subset(predjan, occurrence == 0)
png("janocc_temp_vs_prob.png")
plot(predjanpr$temp_depth, predjanpr$predicted_mthdata, xlab = "temperature", ylab = "probability")
dev.off()
png("janbk_temp_vs_prob.png")
plot(predjanbk$temp_depth, predjanbk$predicted_mthdata, xlab = "temperature", ylab = "probability")
dev.off()
```

@@

mont <- 
data_aeaX <- read.csv("../output/maxent/all_data/pred_file_nov.csv", header = TRUE)
data_aeaX$predicted_mthdata <- NA

xy <- data_aeaX[ ,c(19,20)] # This is to tell R where the coordinates are (in column 18 and 19). Note that the column order needs to be longitude, latitude
data_aea_sp <- SpatialPointsDataFrame(coords = xy, data = data_aeaX, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
avgasc_list <- list.files(paste0("../output/maxent/predictions/nov"), pattern = "^avg_.*.asc", full.names = TRUE) #true means the full path is included
for (j in 1:nrow(data_aea_sp)) { 
for (i in 1:length(avgasc_list)) {  
 de <- data_aea_sp$depthlyr_mod[j]  # a variable for the observation depth layer
  rasdep <- str_sub(avgasc_list[i], 46, -5)
       if (rasdep == de){
          temp_brick <- raster(avgasc_list[i])
        crs(temp_brick) <- aea@crs 
              data_aea_sp$predicted_mthdata[j] <- extract(x=temp_brick, y = data_aea_sp[j, ])

@@

write.csv(data_aea1, "../output/maxent/all_data/pred_file_nov2.csv", row.names = FALSE)
 #}

@@

```{r}
predjul <- read.csv("../output/maxent/all_data/pred_file_jul.csv", header = TRUE)
plot(predjul$occurrence, predjul$predicted_mthdata)
plot(predjul$occurrence, predjul$predicted_alldata, xlab = "occurrence", ylab = "probability", main = "probability for background (o) & occurrence (1) - all data model")
```

@@

```{r}
predlst <- list.files(paste0("../output/maxent/all_data/"), pattern = "pred_file", full.names = TRUE)

for (a in 1:length(predlst)){
  pred <- read.csv(predlst[a])
  mth <- str_sub(predlst[a], 37, -5) 
  predc <- completeFun(pred, "predicted_mthdata")
  predoc <- subset(predc, occurrence == 1)
  predbk <- subset(predc, occurrence == 0)
  png(paste0("monthly_pred_occurrence_", mth, ".png"))
  hmthoc <- hist(predoc$predicted_mthdata, main = paste0("monthly predictions - ", mth, " occurrences"), xlab = "probability of occurrence")
  dev.off() # stops automatic saving of the plot to a png
  png(paste0("monthly_pred_background_", mth, ".png"))
  hmthbk <- hist(predbk$predicted_mthdata, main = paste0("monthly predictions - ", mth, " background"), xlab = "probability of occurrence")
  dev.off() # stops automatic saving of the plot to a png            
  png(paste0("alldata_pred_occurrence_", mth, ".png"))
  halloc <- hist(predoc$predicted_alldata, main = paste0("all data predictions - ", mth, " occurrences"), xlab = "probability of occurrence")
  dev.off() # stops automatic saving of the plot to a png
  png(paste0("alldata_pred_background_", mth, ".png"))
  hallbk <- hist(predbk$predicted_alldata, main = paste0("all data predictions - ", mth, " background"), xlab = "probability of occurrence")
  dev.off() # stops automatic saving of the plot to a png

tss for all data model
```{r}
ev <- evaluate(p = predoc$predicted_alldata , a = predbk$predicted_alldata, model = mod)

tss <- max(ev@TPR + ev@TNR) - 1
tss
```

```{r}
janoc <- read.csv("../output/maxent/all_data/pred_file_jan.csv")
b <- subset(janoc, occurrence == 1)
c <- b$predicted_alldata
a <-max(c, na.rm = TRUE)
a
```

```{r habitat classification on probability - high only}

#binary threshold function
binprob <- function(x){
  ifelse(x >= 0.8, 1,
  ifelse(x < 0.8, 0, NA)) 
}

clogasc_list <- list.files(paste0("../output/maxent/all_data/predictions/july/"), pattern = "^avg_.*.asc", full.names = TRUE)

for (cum in 1:length(clogasc_list)){
  cumascdep <- str_sub(clogasc_list[cum], start = 47, end = -5) #selects the depth from the file name
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cum_mpathr <- calc(cumasc, fun = binprob)
  writeRaster(cum_mpathr, paste0("../output/maxent/all_data/predictions/july/binary_p80_", cumascdep, ".asc"), overwrite = TRUE)
  plot(cum_mpathr, png(paste0("../output/maxent/all_data/predictions/july/binary_p80_", cumascdep, ".png")), overwrite = TRUE)
  dev.off() # stops automatic saving of the plot to a png
  }

```{r binary map averaged 2D representation p80}

binaryclog_list <- list.files(paste0("../output/maxent/all_data/predictions/july/"), pattern = "^binary_p80.*.asc", full.names = TRUE)

binstack <- stack(binaryclog_list)
stacksum <- sum(binstack, na.rm = TRUE)
writeRaster(stacksum, paste0("../output/maxent/all_data/predictions/july/bin_p80_2d.asc"), overwrite=TRUE)
plot(stacksum, png(paste0("../output/maxent/all_data/predictions/july/bin_avg_p80_2d.png")))
dev.off()

```{r}
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
redtrans <- rgb(218, 215, 216, 90, maxColorValue=255) 
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
prpoints <- read.csv("../output/maxent/all_data/pred_file_jul.csv", header = TRUE)
prpoints <- subset(prpoints, occurrence == 1)

prpoints <- completeFun(prpoints, "predicted_mthdata")

pras <- raster("../output/maxent/predictions/jul/bin_p80_2d.asc")
  crs(pras) <- aea@crs
  ascname <- names(pras)
  pras <- calc(pras, fun = binprob)

  pras[pras >0] <- 1

  #lp <- plot(pras, col=rev(colorRampPalette(brewer.pal(10, "Spectral"))(10)), axes = FALSE, box = FALSE, legend = FALSE)
  lp <- plot(pras, axes = FALSE, box = FALSE, legend = FALSE)
  lp <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp <- plot(s, col = "#474646", border = "#474646", add = TRUE)
  lp <- points(prpoints$longitude_meters, prpoints$latitude_meters, add = TRUE, pch=15, cex = 0.5, col = "red")
  print(lp)
  dev.copy(png, ("../output/maxent/all_data/julmth_over0.8.png"), width = 1920,height = 1080)
  dev.off() # stops automatic saving of the plot to a png))

```{r habitat classification on probability - high onlyX}

#binary threshold function
binprob <- function(x){
  ifelse(x >= 0.8, 1,
  ifelse(x < 0.8, 0, NA)) 
}

clogasc_list <- list.files(paste0("../output/maxent/predictions/jul/"), pattern = "^avg_.*.asc", full.names = TRUE)

for (cum in 1:length(clogasc_list)){
  cumascdep <- str_sub(clogasc_list[cum], start = 47, end = -5) #selects the depth from the file name
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cum_mpathr <- calc(cumasc, fun = binprob)
  writeRaster(cum_mpathr, paste0("../output/maxent/predictions/jul/binary_p80_", cumascdep, ".asc"), overwrite = TRUE)
  plot(cum_mpathr, png(paste0("../output/maxent/predictions/jul/binary_p80_", cumascdep, ".png")), overwrite = TRUE)
  dev.off() # stops automatic saving of the plot to a png
  }

```{r binary map averaged 2D representation p80x}

binaryclog_list <- list.files(paste0("../output/maxent/predictions/jul/"), pattern = "^binary_p80.*.asc", full.names = TRUE)

binstack <- stack(binaryclog_list)
stacksum <- sum(binstack, na.rm = TRUE)
writeRaster(stacksum, paste0("../output/maxent/predictions/jul/bin_p80_2d.asc"), overwrite=TRUE)
plot(stacksum, png(paste0("../output/maxent/predictions/jul/bin_avg_p80_2d.png")))
dev.off()

add land to plots with standard legend (working code) THIS WORK!!!
```{r}
aea <- raster("../output/env/aea.tif") #the correct CRS
#maplst <- list.files("../output/maxent/all_data/predictions/", pattern = "binary_avg_2d.*.asc", full.names = TRUE)
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
apr <- aea@crs
brk <- seq(0.1, 1, 0.1) #for legend
redtrans <- rgb(218, 215, 216, 90, maxColorValue=255) 
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis

#r <- raster(avg_77.6112.asc)
#plot(pras)

#for (pred in 1:length(maplst)){
  pras <- raster("../output/maxent/all_data/predictions/apr/avg_77.6112.asc")
  plot(pras)
  crs(pras) <- apr
  ascname <- names(pras)
  #pras[pras >0] <- 1
  lp <- plot(pras, breaks=brk, col=rev(colorRampPalette(brewer.pal(10, "Spectral"))(10)), axes = FALSE, box = FALSE, legend = TRUE)
  lp <- plot(pras)
  lp <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp <- plot(s, col = "#474646", border = "#474646", add = TRUE)
  print(lp)
  dev.copy(png, (paste0("../output/maxent/all_data/predictions/", ascname, pred, ".png")), width = 1920,height = 1080)
  dev.off() # stops automatic saving of the plot to a png))
#}

barcharts showing probability distribution at depth

first bin the probabilities for cells inside the mcp
```{r bin probabilities}
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
clogasc_list <- list.files(paste0("../output/maxent/predictions/nov/"), pattern = "^avg_cloglog_.*.asc", full.names = TRUE)

binprob <- function(x){
  ifelse(x > 0 & x < 0.1, 0.1,
  ifelse(x <= 0, 0, NA))
}

for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
  probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
  writeRaster(probbin, paste0("../output/maxent/predictions/nov/binned_1_avgprob_", ascname, ".asc"), overwrite = TRUE)
  plot(probbin, png(paste0("../output/maxent/predictions/nov/binned_1_avgprob_", ascname, ".png")), overwrite = TRUE)
  dev.off() # stops automatic saving of the plot to a png
}

binprob <- function(x){
  ifelse(x >= 0.1 & x < 0.2, 0.2,
  ifelse(x <= 0, 0, NA))
}

for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
  probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
  writeRaster(probbin, paste0("../output/maxent/predictions/nov/binned_2_avgprob_", ascname, ".asc"), overwrite = TRUE)
  plot(probbin, png(paste0("../output/maxent/predictions/nov/binned_2_avgprob_", ascname, ".png")), overwrite = TRUE)
  dev.off() # stops automatic saving of the plot to a png
}

binprob <- function(x){
  ifelse(x >= 0.2 & x < 0.3, 0.3,
  ifelse(x <= 0, 0, NA))
}

for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
  probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
  writeRaster(probbin, paste0("../output/maxent/predictions/nov/binned_3_avgprob_", ascname, ".asc"), overwrite = TRUE)
  plot(probbin, png(paste0("../output/maxent/predictions/nov/binned_3_avgprob_", ascname, ".png")), overwrite = TRUE)
  dev.off() # stops automatic saving of the plot to a png
}

binprob <- function(x){
  ifelse(x >= 0.3 & x < 0.4, 0.4,
  ifelse(x <= 0, 0, NA))
}

for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
  probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
  writeRaster(probbin, paste0("../output/maxent/predictions/nov/binned_4_avgprob_", ascname, ".asc"), overwrite = TRUE)
  plot(probbin, png(paste0("../output/maxent/predictions/nov/binned_4_avgprob_", ascname, ".png")), overwrite = TRUE)
  dev.off() # stops automatic saving of the plot to a png
}

binprob <- function(x){
  ifelse(x >= 0.4 & x < 0.5, 0.5,
  ifelse(x <= 0, 0, NA))
}

for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
  probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
  writeRaster(probbin, paste0("../output/maxent/predictions/nov/binned_5_avgprob_", ascname, ".asc"), overwrite = TRUE)
  plot(probbin, png(paste0("../output/maxent/predictions/nov/binned_5_avgprob_", ascname, ".png")), overwrite = TRUE)
  dev.off() # stops automatic saving of the plot to a png
}

binprob <- function(x){
  ifelse(x >= 0.5 & x < 0.6, 0.6,
  ifelse(x <= 0, 0, NA))
}

for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
  probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
  writeRaster(probbin, paste0("../output/maxent/predictions/nov/binned_6_avgprob_", ascname, ".asc"), overwrite = TRUE)
  plot(probbin, png(paste0("../output/maxent/predictions/nov/binned_6_avgprob_", ascname, ".png")), overwrite = TRUE)
  dev.off() # stops automatic saving of the plot to a png
}

binprob <- function(x){
  ifelse(x >= 0.6 & x < 0.7, 0.7,
  ifelse(x <= 0, 0, NA))
}

for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
  probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
  writeRaster(probbin, paste0("../output/maxent/predictions/nov/binned_7_avgprob_", ascname, ".asc"), overwrite = TRUE)
  plot(probbin, png(paste0("../output/maxent/predictions/nov/binned_7_avgprob_", ascname, ".png")), overwrite = TRUE)
  dev.off() # stops automatic saving of the plot to a png
}

binprob <- function(x){
  ifelse(x >= 0.7 & x < 0.8, 0.8,
  ifelse(x <= 0, 0, NA))
}

for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
  probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
  writeRaster(probbin, paste0("../output/maxent/predictions/nov/binned_8_avgprob_", ascname, ".asc"), overwrite = TRUE)
  plot(probbin, png(paste0("../output/maxent/predictions/nov/binned_8_avgprob_", ascname, ".png")), overwrite = TRUE)
  dev.off() # stops automatic saving of the plot to a png
}

binprob <- function(x){
  ifelse(x >= 0.8 & x < 0.9, 0.9,
  ifelse(x <= 0, 0, NA))
}

for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
  probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
  writeRaster(probbin, paste0("../output/maxent/predictions/nov/binned_9_avgprob_", ascname, ".asc"), overwrite = TRUE)
  plot(probbin, png(paste0("../output/maxent/predictions/nov/binned_9_avgprob_", ascname, ".png")), overwrite = TRUE)
  dev.off() # stops automatic saving of the plot to a png
}

binprob <- function(x){
  ifelse(x >= 0.9 & x <= 1, 1,
  ifelse(x <= 0, 0, NA))
}

for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
  probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
  writeRaster(probbin, paste0("../output/maxent/predictions/nov/binned_10_avgprob_", ascname, ".asc"), overwrite = TRUE)
  plot(probbin, png(paste0("../output/maxent/predictions/nov/binned_10_avgprob_", ascname, ".png")), overwrite = TRUE)
  dev.off() # stops automatic saving of the plot to a png
}

get data to plot probability by depth... need to do manually 1-10
```{r}
ascdepth_list_high <- list.files(paste0("../output/maxent/predictions/nov/"), pattern = "^binned_1_avgprob_.*asc", full.names = TRUE)

binprob <- function(x){
  ifelse(x >0,  1,
  ifelse(x == -9999, 0, NA))
}

binaryavgstack <- stack(ascdepth_list_high)
stackstathigh <- data.frame(matrix(ncol = 2, nrow = nlayers(binaryavgstack)))
stackstathigh[ ,1] <- c(1:49)
colnames(stackstathigh) <- c("asclayer", "prob_bin")

for (lyr in 1:nlayers(binaryavgstack)){
  ascname <-  str_sub(ascdepth_list_high[lyr], 63, -5)
  dlay <- binaryavgstack[[lyr]]
  dlay <- calc(dlay, fun = binprob) #creates raster layer with cell values based on the binprob function
  lyrsum <- cellStats(dlay, sum)
  stackstathigh$prob_bin[lyr] <- lyrsum
  stackstathigh$asclayer[lyr] <- ascname

}
write.csv(stackstathigh, paste0("../output/maxent/predictions/nov/probbin_1_cellcount_bydepth_avg.csv"), row.names = FALSE)

probblst <- list.files(paste0("../output/maxent/predictions/nov"), pattern = "^probbin_.*.csv", full.names = TRUE)
a <- read.csv(probblst[1])
b <- read.csv(probblst[2])
c <- read.csv(probblst[3])
d <- read.csv(probblst[4])
e <- read.csv(probblst[5])
f <- read.csv(probblst[6])
g <- read.csv(probblst[7])
h <- read.csv(probblst[8])
i <- read.csv(probblst[9])
j <- read.csv(probblst[10])

stackstat <- cbind(a, b[ ,2], c[ ,2], d[ ,2], e[ , 2], f[ ,2], g[ ,2], h[ ,2], i[ ,2], j[ ,2])
colnames(stackstat) <- c("depth", "0 - 0.09", "0.1 - 0.19", "0.2 - 0.29", "0.3 - 0.39", "0.4 - 0.49", "0.5 - 0.59", "0.6 - 0.69", "0.7 - 0.79", "0.8 - 0.89", ">0.9")
stackstat <- melt(stackstat, id = "depth")
stackstat <- stackstat[!(stackstat$depth == "1151.99"), ]
stackstat <- stackstat[!(stackstat$depth == "1265.86"), ]
stackstat <- stackstat[!(stackstat$depth == "1387.38"), ]

colnames(stackstat) <- c("Depth", "Probability", "Cells")

write.csv(stackstat, paste0("../output/maxent/predictions/nov/allprobbin_cellcount_bydepth_avg.csv"), row.names = FALSE)

count number of cells that are not NA in each raster layer that are inside the mcp

```{r}
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
clogasc_list <- list.files(paste0("../output/maxent/predictions/nov/"), pattern = "^avg_cloglog_.*.asc", full.names = TRUE)
cumst <- data.frame(0, 0)
colnames(cumst) <- c("depth", "no_cells")

for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cumst[cum, 1] <- str_sub(ascname, 13)
  cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
  ccnt <- freq(cumasc, useNA='no')
  ccnt <- sum(ccnt[ ,2])
  cumst[cum, 2] <- ccnt
}

cumst$depth <- as.numeric(cumst$depth)
cumst1 <- cumst[order(cumst$no_cells), ]

write.csv(cumst1, "../output/maxent/predictions/nov/cellsperlayer.csv", row.names = FALSE)

think about how to get proportions...

```{r}
pr <- read.csv("../output/maxent/predictions/nov/allprobbin_cellcount_bydepth_avg.csv", header = TRUE)
cumst1 <- read.csv("../output/maxent/predictions/nov/cellsperlayer.csv", header = TRUE)

#order both filed from high to low depth
pr <- pr[order(pr$Depth), ]
cumst1 <- cumst[order(cumst$depth), ]

#so there are some differences in the depth numbers... use partial matching to get the number of cells on each layer

a <- pr
for (r in 1:nrow(pr)){
  d1 <- str_sub(pr$Depth[r], end = 4)
  for (ro in 1:nrow(cumst1)){
    d2 <- str_sub(cumst1$depth[ro], end = 4)
    if (d1 == d2){
        a$total_cells[r] <- cumst1$no_cells[ro]
    }
  }
}

# now work out percentage of cells for each probability

for (r in 1:nrow(a)){
  a$p_cells[r] <- (a$Cells[r]/a$total_cells[r])*100
}

write.csv(a, "../output/maxent/predictions/nov/dis_prob_cells.csv", row.names = FALSE)

histogram of probability by depth (straight count)

```{r}
mthna = "nov"
bydepth <- ggplot(data = a, aes(x = Depth, y = Cells, fill = Probability)) + geom_bar(stat = "identity") +   scale_x_reverse() + coord_flip()
png(paste0("../output/maxent/predictions/", mthna, "/depthplot_probavg.png"))
print(bydepth)
dev.off()
```

histogram of probability by depth - by proportion

bydepth <- ggplot(a, aes(Depth, p_cells, fill = Probability)) + geom_col() + scale_x_reverse() + coord_flip() #XXXXXcareful - the deeper layers aren't being displayed correctly here
plot(bydepth)
png(paste0("../output/maxent/predictions/", mthna, "/depthplot_probavg_prop.png"))
print(bydepth)
dev.off()
```

ok lets try get an probability for the whole month

```{r}
a <- read.csv("../output/maxent/predictions/jul/dis_prob_cells.csv", header = TRUE)

#subset the probability ranges
p1 <- subset(a, Probability == "0 - 0.09")
p2 <- subset(a, Probability == "0.1 - 0.19")
p3 <- subset(a, Probability == "0.2 - 0.29")
p4 <- subset(a, Probability == "0.3 - 0.39")
p5 <- subset(a, Probability == "0.4 - 0.49")
p6 <- subset(a, Probability == "0.5 - 0.59")
p7 <- subset(a, Probability == "0.6 - 0.69")
p8 <- subset(a, Probability == "0.7 - 0.79")
p9 <- subset(a, Probability == "0.8 - 0.89")
p10 <- subset(a, Probability == ">0.9")

#count the number of cells per probability.

cp1 <- sum(p1$Cells)
cp2 <- sum(p2$Cells)
cp3 <- sum(p3$Cells)
cp4 <- sum(p4$Cells)
cp5 <- sum(p5$Cells)
cp6 <- sum(p6$Cells)
cp7 <- sum(p7$Cells)
cp8 <- sum(p8$Cells)
cp9 <- sum(p9$Cells)
cp10 <- sum(p10$Cells)

tc2 <- sum(cp1, cp2, cp3, cp4, cp5, cp6, cp7, cp8, cp9, cp10) #how many cells in total for novy have a value
tcell <- sum(p1$total_cells) # how many cells are available to have a value...
#tc2 and tcell should match

#create datbase of total cells per probability bin for the month

b <- unique(a$Probability) #get the unique probability bins
c <- as.data.frame(rbind(cp1, cp2,  cp3, cp4, cp5, cp6, cp7, cp8, cp9, cp10))
c$probability <- b
colnames(c) <- c("cells", "prob_bin")
rownames(c) <- c()
c$month <- "jul"
```

make plot of probability over the month
```{r}
pmth <- ggplot(d, aes(month, cells, fill = prob_bin)) + geom_bar(stat='identity') 
plot(pmth)
png(paste0("../output/maxent/predictions/", mthna, "/prob_avg_mth.png"))
print(pmth)
dev.off()
```

merge two months of data together into one file then plot

```{r}
f <- rbind(c, d)
pmth <- ggplot(f, aes(month, cells, fill = prob_bin)) + geom_bar(stat='identity') 
plot(pmth)
png(paste0("../output/maxent/predictions/prob_avg_mth_test.png"))
print(pmth)
dev.off()
```

boxplot of test auc scores test

```{r}
dec <- read.csv("../output/maxent/models/decavgAIC.csv", header = TRUE)
mar <- read.csv("../output/maxent/models/maravgAIC.csv", header = TRUE)
apr <- read.csv("../output/maxent/models/apravgAIC.csv", header = TRUE)
may <- read.csv("../output/maxent/models/mayavgAIC.csv", header = TRUE)
jun <- read.csv("../output/maxent/models/junavgAIC.csv", header = TRUE)
jul <- read.csv("../output/maxent/models/julavgAIC.csv", header = TRUE)
aug <- read.csv("../output/maxent/models/augavgAIC.csv", header = TRUE)
sep <- read.csv("../output/maxent/models/sepavgAIC.csv", header = TRUE)
oct <- read.csv("../output/maxent/models/octavgAIC.csv", header = TRUE)
nov <- read.csv("../output/maxent/models/novavgAIC.csv", header = TRUE)

mar <- mar$test_AUC
mar <- head(mar, -1)
apr <- apr$test_AUC
apr <- head(apr, -1)
may <- may$test_AUC
may <- head(may, -1)
jun <- jun$test_AUC
jun <- head(jun, -1)
jul <- jul$test_AUC
jul <- head(jul, -1)
aug <- aug$test_AUC
aug <- head(aug, -1)
sep <- sep$test_AUC
sep <- head(sep, -1)
oct <- oct$test_AUC
oct <- head(oct, -1)
nov <- nov$test_AUC
nov <- head(nov, -1)
dec <- dec$test_AUC
dec <- head(dec, -1)

n <- max(length(mar), length(apr), length(may), length(jun), length(jul), length(aug), length(sep), length(oct), length(nov), length(dec))
length(mar) <- n                      
length(apr) <- n
length(may) <- n
length(jun) <- n
length(jul) <- n
length(aug) <- n
length(sep) <- n
length(oct) <- n
length(nov) <- n
length(dec) <- n

testauc <- cbind(mar, apr, may, jun, jul, aug, sep, oct, nov, dec)
colnames(c) <-c("Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")

boxplot of train auc scores test

```{r}
dec <- read.csv("../output/maxent/models/decavgAIC.csv", header = TRUE)
mar <- read.csv("../output/maxent/models/maravgAIC.csv", header = TRUE)
apr <- read.csv("../output/maxent/models/apravgAIC.csv", header = TRUE)
may <- read.csv("../output/maxent/models/mayavgAIC.csv", header = TRUE)
jun <- read.csv("../output/maxent/models/junavgAIC.csv", header = TRUE)
jul <- read.csv("../output/maxent/models/julavgAIC.csv", header = TRUE)
aug <- read.csv("../output/maxent/models/augavgAIC.csv", header = TRUE)
sep <- read.csv("../output/maxent/models/sepavgAIC.csv", header = TRUE)
oct <- read.csv("../output/maxent/models/octavgAIC.csv", header = TRUE)
nov <- read.csv("../output/maxent/models/novavgAIC.csv", header = TRUE)

mar <- mar$train_AUC
mar <- head(mar, -1)
apr <- apr$train_AUC
apr <- head(apr, -1)
may <- may$train_AUC
may <- head(may, -1)
jun <- jun$train_AUC
jun <- head(jun, -1)
jul <- jul$train_AUC
jul <- head(jul, -1)
aug <- aug$train_AUC
aug <- head(aug, -1)
sep <- sep$train_AUC
sep <- head(sep, -1)
oct <- oct$train_AUC
oct <- head(oct, -1)
nov <- nov$train_AUC
nov <- head(nov, -1)
dec <- dec$train_AUC
dec <- head(dec, -1)

n <- max(length(mar), length(apr), length(may), length(jun), length(jul), length(aug), length(sep), length(oct), length(nov), length(dec))
length(mar) <- n                      
length(apr) <- n
length(may) <- n
length(jun) <- n
length(jul) <- n
length(aug) <- n
length(sep) <- n
length(oct) <- n
length(nov) <- n
length(dec) <- n

trainauc <- cbind(mar, apr, may, jun, jul, aug, sep, oct, nov, dec)
colnames(c) <-c("Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")
```

boxplot of cbi

```{r}
dec <- read.csv("../output/maxent/models/decavgAIC.csv", header = TRUE)
mar <- read.csv("../output/maxent/models/maravgAIC.csv", header = TRUE)
apr <- read.csv("../output/maxent/models/apravgAIC.csv", header = TRUE)
may <- read.csv("../output/maxent/models/mayavgAIC.csv", header = TRUE)
jun <- read.csv("../output/maxent/models/junavgAIC.csv", header = TRUE)
jul <- read.csv("../output/maxent/models/julavgAIC.csv", header = TRUE)
aug <- read.csv("../output/maxent/models/augavgAIC.csv", header = TRUE)
sep <- read.csv("../output/maxent/models/sepavgAIC.csv", header = TRUE)
oct <- read.csv("../output/maxent/models/octavgAIC.csv", header = TRUE)
nov <- read.csv("../output/maxent/models/novavgAIC.csv", header = TRUE)

mar <- mar$cbi
mar <- head(mar, -1)
apr <- apr$cbi
apr <- head(apr, -1)
may <- may$cbi
may <- head(may, -1)
jun <- jun$cbi
jun <- head(jun, -1)
jul <- jul$cbi
jul <- head(jul, -1)
aug <- aug$cbi
aug <- head(aug, -1)
sep <- sep$cbi
sep <- head(sep, -1)
oct <- oct$cbi
oct <- head(oct, -1)
nov <- nov$cbi
nov <- head(nov, -1)
dec <- dec$cbi
dec <- head(dec, -1)

n <- max(length(mar), length(apr), length(may), length(jun), length(jul), length(aug), length(sep), length(oct), length(nov), length(dec))
length(mar) <- n                      
length(apr) <- n
length(may) <- n
length(jun) <- n
length(jul) <- n
length(aug) <- n
length(sep) <- n
length(oct) <- n
length(nov) <- n
length(dec) <- n

cbi <- cbind(mar, apr, may, jun, jul, aug, sep, oct, nov, dec)
colnames(c) <-c("Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")
```
